Importance of depth refugia for reef resilience and intervention on the Great Barrier Reef under future climate change

### 2025-10-05 paper/paper_draft.qmd
Updates to acknowledgements section

We acknowledge the contributions of Barbara Robson and Jessica Benthuysen to manuscript
preparation. This research was funded by the Reef Restoration and Adaptation Program, and
facilitated by the Australian Institute of Marine Science. We acknowledge thermal projection
data sourced from HighResCoralStress datasets, model parameterisation data sourced from the
Ecological Intelligence for Reef Restoration (EcoRRAP) subprogram, larval transition
probability data derived from the eReefs GBR1 hydrodynamic model, and spatial and depth data
available from the Great Barrier Reef Marine Park Authority. All authors are funded by the
Reef Restoration and Adaptation Program **\[BG: To be completed.\]**.

>>>>

The authors acknowledge the Bindal people, Traditional Owners of the land on which the work
took place at the AIMS Townsville site. The authors acknowledge the contributions of Barbara
Robson and Jessica Benthuysen to manuscript preparation. This research was funded by the
Reef Restoration and Adaptation Program, and facilitated by the Australian Institute of
Marine Science. The authors acknowledge thermal projection data sourced from
HighResCoralStress datasets, model parameterisation data sourced from the Ecological
Intelligence for Reef Restoration (EcoRRAP) subprogram, larval transition probability data
derived from the eReefs GBR1 hydrodynamic model, and spatial and depth data available from
the Great Barrier Reef Marine Park Authority. The eReefs Project is a private-public
collabroation between Australia's leading operational and scientific research agencies,
government and corporate Australia. All authors are funded by the Reef Restoration and
Adaptation Program **\[BG: To be completed.\]**.
